---
title: "2019 SIPS Grad Student Climate Survey Results"
author: "Survey authored by Janani Hariharan, results compiled by Ellie Taagen"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(dplyr)
library(magrittr)
library(wesanderson)
```
***  
```{r Survey import, include=FALSE}
Survey <- read.csv("~/Dropbox/Cornell/Dept of Plant Breeding/GSC2019survey.csv", header = TRUE)
```

> In 2019 the School of Integrative Plant Science (SIPS) graduate student council developed a survey to assess the SIPS graduate students satisfaction and concerns with unification of the five sections, career path exploration, mental health resources and inclusion initiatives. The survey was distributed via the SIPS graduate student listserv (179 students). The 47 participant's responses are summarized below. 

#### 1) Should there be an introductory curriculum for all incoming SIPS graduate students and if yes, what should the classes be? (37 responses)  
```{r Q1, echo = FALSE}
ggplot(data = Survey[Survey$Question==1,], aes(Response, fill= Response))+
  geom_bar()+
  scale_fill_manual(values = wes_palette("FantasticFox1"))+
  theme_classic()+
  theme(legend.position = "none",text = element_text(size=15))+
  xlab("")

```

**Suggested topics for core curriculum class:**  

* Exposure to general research in SIPS  
* Opportunity to meet students from other SIPS sections  
* Grant writing seminar   
* Introduction to graduate school (scientific writing, presentation skills, teaching pedagogy. RCR, TAing advice, research methods, statistics, communication, leadership and mentorship skills)  

*** 

#### 2) How can we increase interactions between graduate students from different sections?  
```{r Q2, include = FALSE}
library(scales)
bp<- ggplot(data = Survey[Survey$Question==2,], aes(x="", y=Value, fill= Response))+ 
  geom_bar(width = 1, stat = "identity")
pie <- bp + coord_polar("y", start=0)

blank_theme <- theme_minimal()+
  theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=14, face="bold")
  )
```
```{r, echo=FALSE}
pie + scale_fill_manual(values = wes_palette("FantasticFox1")) + blank_theme +
  theme(axis.text.x=element_blank())+
  geom_text(aes(y = Value/3 + c(0, cumsum(Value)[-length(Value)]), 
                label = percent(Value/100)), size=5)
```

**Suggested joint social events:**  

* Greenhouse parties  
* Bowling nights, board game nights   
* Head to TGIF at the Big Red Barn together   
* Revive PPPMB's Cheers with your Peers or make our own SNEEB  
* “Meals with Strangers” where 4-5 graduate students from different sections are matched up and given a dinner allowance   

**Suggested joint academic events:**  

* Joint section lightning talks   
* Grad student colloquium  

*** 

#### 3) Do you have any suggestions for the SIPS building renovations that would be helpful for graduate students?   

<span style="color: royalblue">**Bradfield renovations:** </span>   

* *"Greater transparency about plans, expected changes and timelines, especially with time-sensitive nature of some experiments."* 
* *"Windows (for Bradfield occupants)."*  
* *"More power outlets at the ends of the halls in Bradfield."* 
* *"Gender neutral bathrooms, and more even distribution of M/F bathrooms in Bradfield Hall."*  

<span style="color: mediumseagreen">**Accessible common areas:** </span>   

* *"Common meeting spaces exclusively for graduate students, with comfortable chairs, tables and desks. The goal of such a space is to increase grad wellness and socializing."*  
* *"Accessibility for non-hearing grad students: open spaces where people can see each other and communicate, less noisy ventilation and heating systems, high contrast stairs."*  
* *"Additional privacy/accessibility: bright lights that don’t cause eyestrain, cloth dividers to ensure privacy and mute noise, more ergonomic seating."*  

<span style="color: Orange">**Anti-common lab spaces:** </span>     

* *"Communal lab spaces would kill productivity and create resentment among lab groups, possibly reducing peer interaction."*  
* *“Getting work done for your thesis/dissertation is hard enough without also being plopped into an open space with little privacy, or worse, having to tiptoe around other people in the same lab. The workplace does not need to be the venue for social interaction, or even for professional connection-making.”*  

*** 

#### 4) What do you think about the application and review process for the Schmittau-Novak Small Grants Program?  
> Respondents had either not heard of / not applied, and hence did not know anything about it, or had **positive opinions** about the program. They thought it was fair and offered good feedback, efficient, promoted collaborations within SIPS, and that it was one of the **few funding options open to non US citizens**.  One respondent mentioned wanting **more reminders** so that they could plan their application better, and another mentioned lack of clarity about the review process.  

*** 

#### 5) How can SIPS support graduate students in mentoring undergraduates?  

* *"Could mentoring an undergraduate count towards a teaching requirement or course credits?"*  

* *"Setting clear expectations on mentoring, aided by mentorship training."*  

* *"Creating a common SIPS webpage where graduate students or PIs looking for undergrads would post details of project and pay. This could be promoted via undergrad listservs."*  

* *"Greater connection with undergrads wanting research experience through listservs or online forums, connecting with undergraduate research organizations."*   

* *"GSMU-style dinners and mentorship programs."*  

* *"Provide funding specifically for undergraduate mentoring."*   

* *"Impostor syndrome is a barrier to mentoring undergrads."*  

* *"Support from PI with the mentoring process: Flexibility to say no, autonomy to pursue independent ideas with undergraduate research project."* 

* *"The Schmittau-Novak program was mentioned as a good way to promote undergraduate mentoring."*  

* Some respondees mentioned having plenty of undergraduate mentees and having no questions about the mentoring process.

*** 

#### 6) Are you interested in extension or international training/jobs and if yes, how should information about jobs/training be made available? (33 responses) 

```{r Q6, echo=FALSE} 
ggplot(data = Survey[Survey$Question==6,], aes(Response, fill= Response))+
  geom_bar()+
  scale_fill_manual(values = wes_palette("FantasticFox1"))+
  theme_classic()+
  theme(legend.position = "none",text = element_text(size=15))+
  xlab("")
```

**Yes, and:**  

* Communicate via a central website that students could also contribute to, i.e. Slack  
* Email listserv (Magdalen's emails, section chair)  
* Panel and advice from faculty with similar career backgrounds  
* Increased opportunities for grad students through established programs, i.e.Cornell Cooperative Extension  

*** 

#### 7) What type of careers are you interested in? Pick all that apply.  

```{r Q7, echo=FALSE}
ggplot(data = Survey[Survey$Question==7,], aes(Response, fill= Response))+
  geom_bar()+
  scale_fill_manual(values = c( "plum","palevioletred1", "firebrick", "darkorange", "goldenrod2", "mediumaquamarine", "olivedrab4", "skyblue2", "steelblue4", "orchid4", "purple4", "gray38"))+
  theme_classic()+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

*** 

#### 8) How can SIPS support students in learning about and preparing for different careers?  

* *"Utilize the BEST program more."*  
 
* *"Make internships or industry experiences more common."*  

* *"Invite seminar speakers from non-academic backgrounds."*  

* *"Mentor pairing for different careers with SIPS alumni."*  

* *"Promote existing resources for professional development like career fairs or library workshops. Lunchtime career chats with scientists working in non-academic roles."*  

* *"Encourage students to take 1 class per semester that isn’t directly related to their thesis work."*  

* *"SIPS should require students to do more career exploration. Making this mandatory will discourage PIs from interfering with this process."*  

***  

#### 9) How can SIPS support graduate student mental health and wellbeing?  

**Training**  

* *"Sensitivity training for advisors."*  

* *"Improve clarity on graduate student expectations and requirements. It is sometimes unclear who is the right person to ask which question, or set up a time to meet them."*  

* *"Official time off policy for graduate students."*  

* *"Formalize TA and RA expectations."*  

* *"Follow a do-no-harm policy and allow for flexibility and time to let students take care of their own mental health."*  

**Engagement**  

* *"Have advisors check in about work-life balance and mental health."*  

* *"Clear instructions to TAs and professors on how to deal with mental health issues."*  

* *"Regular meetings between DGS and graduate students."*  

* *"Active discouragement of “70 hour week” culture by faculty and staff."*  

* *"Remove mandatory duties or commitments in Ithaca for Geneva-based students. It can be hard to be a part of both communities, and some people would like to focus on strengthening bonds with the existing Geneva community."*  

* *"Round table, structured group discussion on mental health led by students."*   

**Expansion of resources**  

* *"Mental health support at off-campus locations like Cornell AgriTech."*  

* *"Windows in Bradfield Hall."*  

* *"Hire new faculty with strong mentorship skills or interests."*  

* *"Focus on chronic stressors instead of acute stressors, i.e. long-term issues that could be aided with therapy."*  

* *"Build a sense of community with other graduate students."*   

***  

#### 10) Does SIPS have an efficient process for dealing with bias and/or harassment incidents? If no, what could be improved?  

> # <span style="color: Red"> 29/30 respondees were not aware of what policies SIPS had in place to combat bias or harassment in the workplace </span>   

**What could be improved:**  

* Publicized protocol on what to do when faced with such an incident  
* Address concerns about retaliation when filing complaints  
* Rectify the feeling that people in power will not take the complaint seriously
* Establish protocol on who to talk to if being harassed, i.e. SIPS ombudsman  
* Train staff on confidentiality and conflict resolution  

***  

#### 11) Have you seen an improvement in SIPS' commitment to diversity and inclusion over the last 2 years? If not, what more needs to be done?  
```{r Q11, echo=FALSE}
ggplot(data = Survey[Survey$Question==11,], aes(Response, fill= Response))+
  geom_bar()+
  scale_fill_manual(values = wes_palette("FantasticFox1"))+
  theme_classic()+
  theme(legend.position = "none",text = element_text(size=15))+
  xlab("")
```

**Listed concerns about what more needs to be done:** 

* Lack of sensitivity training for professors and teaching staff   
* Little follow-through on conversations related to D&I   
* Some sections still use the GRE as a requirement for applications    
* SIPS ABC is very slow to shift the dial  
* Lack of participation from graduate students in SIPS ABC  
* Lack of updates from SIPS ABC to the general SIPS audience    
* Funds for international students to visit Cornell and SIPS   
* Resistance from faculty towards harassment training creates an unwelcome environment for minorities in SIPS   
* Lack of representation in SIPS faculty  
  + Absence of faculty of color was specifically noted  
  + This leads to lack of appropriate mentorship and lack of belonging  